Notes on Hartree-Fock Stability of HEG

### 2016-07-25 overview/heg_equations.tex
Pushed functionality to the class level within .pyx. The calc is started by __init__(args) and is greatly simplified at the python level.

\begin{equation}\label{eq:hfexch}
\epsilon_{k\sigma}^{(x)} = -\frac{2e^2k_{F\sigma}}{\pi}f_{ND}\left(\frac{k}{k_{F\sigma}}\right),
\end{equation}
where in 3D, the function $f_{3D}$ is given by
\begin{equation}
f_{3D}\left(y\right) = \frac{1}{2} + \frac{1-y^2}{4y} ln \left|\frac{1+y}{1-y} \right|,
\end{equation}
and in 2D, it is
\begin{equation}\label{eq:fnd}
f_{2D}\left(y\right) = 
\begin{cases} 
    \mathbf{E}\left(y\right), &  y \leq 1, \\
    y 
    \left[ 
        \mathbf{E} 
        \left(
            \frac{1}{y} 
        \right)
        -
        \left(
            1 - \frac{1}{y^2}
        \right)
        \mathbf{K}
        \left(
            \frac{1}{y}
        \right)
       \right]  ,& y \geq 1. 
\end{cases}
\end{equation}
The functions $\mathbf{K}(y)$ and $ \mathbf{E}(y) $ are complete elliptic integrals of the first and second kind, respectively. These are implemented in SciPy as \emph{scipy.special.ellipk} and \emph{scipy.special.ellipe}.

>>>>

\begin{equation}\label{eq:hfexch}
\epsilon_{k\sigma}^{(x)} = -\frac{2e^2k_{F\sigma}}{\pi}f_{ND}\left(\frac{k}{k_{F\sigma}}\right),
\end{equation}
where in 3D, the function $f_{3D}$ is given by
\begin{equation}
f_{3D}\left(y\right) = \frac{1}{2} + \frac{1-y^2}{4y} ln \left|\frac{1+y}{1-y} \right|,
\end{equation}
and in 2D, it is
\begin{equation}\label{eq:fnd}
f_{2D}\left(y\right) = 
\begin{cases} 
    \mathbf{E}\left(y\right), &  y \leq 1, \\
    y 
    \left[ 
        \mathbf{E} 
        \left(
            \frac{1}{y} 
        \right)
        -
        \left(
            1 - \frac{1}{y^2}
        \right)
        \mathbf{K}
        \left(
            \frac{1}{y}
        \right)
       \right]  ,& y \geq 1. 
\end{cases}
\end{equation}
The functions $\mathbf{K}(y)$ and $ \mathbf{E}(y) $ are complete elliptic integrals of the first and second kind, respectively. These are implemented in SciPy as \emph{scipy.special.ellipk} and \emph{scipy.special.ellipe}. After a significant struggle, I have found that the author of the textbook\cite{Guiliani2005} and scipy/wolfram use a different definition of the complete elliptic integral. I was able to reproduce the graphs on pages 82 and 83 of \cite{Guiliani2005} properly with $\mathbf{K}(x) \rightarrow \mathbf{K}(x^2)$ and $\mathbf{E}(x) \rightarrow \mathbf{E}(x^2)$.
